---
title: "Exploring Maps in R"
author: "`r Sys.getenv('USER')`"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    code_fold: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning=FALSE,
                      fig.height=3.5,
                      fig.width=6)

library(tidyverse)
library(lubridate)
library(here)
library(PerformanceAnalytics)
library(plotly)
library(scales)
library(gridExtra)
library(DT)
## for mapping
library(ggmap)
library(maps)
library(mapproj)
library(cowplot)
```

## Map Explore

Exploring different map options. Focus on how maps are represented BEFORE data applied.

#### Setup 

Most accessible option:

* **maps**, **ggmaps** packages, using **get_map()** to fetch coordinates of interest.
* **ggplot2** for display, using **geom_map** or **geom_polygon**.
* two main map sources: **Google**, **Stamen**.
    + Stamen has some good controls and is more artistic.
    + Google is *much* faster.

Note that with ggmap/get_map it appears that Houston, Texas is the default(?). If inputs aren't accepted, it shows Houston area. (at least that happened in my first session)

### Country

#### Google

Easy but not a great projection.

```{r}
## can use place names
ctry_gg <- get_map(location='Canada', zoom=3)
ggmap(ctry_gg)
```

#### Stamen

Need to use coordinates, which gives more control. Also not a great projection.

```{r}
ctry_s <- get_stamenmap(c(top=75, right=-51, bottom=41, left=-143), zoom=4)
ggmap(ctry_s)
```

### Province

Google has several styles - covered further below.

```{r}
prov_gg <- get_map(location='British Columbia', zoom=5, maptype='roadmap')
ggmap(prov_gg)
```

### City

Vancouver:

* longitude: 123.1207° W
* latitude: 49.2827° N

#### Stamen 

Zoom settings determine the resolution.

Vancouver by longitude / latitude boundary:

```{r}
## stamen based on bounding box - nice!
van_s1 <- get_stamenmap(bbox=c(top=49.35, right=-123, bottom=49.18, left=-123.3), zoom=12)
ggmap(van_s1)
```

```{r}
## adjust bounding box
van_s2 <- get_stamenmap(bbox=c(top=49.33, right=-123.05, bottom=49.24, left=-123.25), zoom=14)
ggmap(van_s2)
```

```{r}
van_s3 <- get_stamenmap(bbox=c(top=49.318, right=-123.085, bottom=49.26, left=-123.172), zoom=15)
ggmap(van_s3)
```

Different map types

* terrain (default)
* watercolor: as name implies
* toner: hard black/white

```{r}
van_s2w <- get_stamenmap(bbox=c(top=49.33, right=-123.05, bottom=49.24, left=-123.25), zoom=14, maptype='watercolor')
ggmap(van_s2w)
```

Toner - pretty cool!

```{r}
#van_s2t <- get_stamenmap(bbox=c(top=49.33, right=-123.05, bottom=49.24, left=-123.25), zoom=14, maptype='toner')
van_s2t <- get_stamenmap(bbox=c(top=49.318, right=-123.085, bottom=49.26, left=-123.172), zoom=15, maptype='toner')
ggmap(van_s2t)
```


#### Google

```{r}
## Google: need API key - stored if local file listed in .gitignore so not in repo
source('gmk.R')
```

With Google, can use regular names, not just coordinates.

```{r}
## google
van_gg <- get_map(location='vancouver, british columbia')
ggmap(van_gg)
```

Can use coordinates as well.

```{r}
## google: locaction with 2 coords - doesn't seem to work with boundary
van_gg2 <- get_map(location=c(lon=-123.1, lat=49.35))
ggmap(van_gg2)
```

Can control with two coordinates and zoom:

```{r}
van_gg3 <- get_map(location=c(lon=-123.13, lat=49.28), zoom=13)
ggmap(van_gg3)
```

Different map types available:

* terrain (default)
* satellite
* roadmap
* hybrid (seems same as roadmap?)

```{r}
van_gg3s <- get_map(location=c(lon=-123.13, lat=49.28), zoom=13, maptype='satellite')
ggmap(van_gg3s)
```

Roadmap

```{r}
van_gg3r <- get_map(location=c(lon=-123.13, lat=49.28), zoom=13, maptype='roadmap')
ggmap(van_gg3r)
```

### Address

#### Google 

Can zoom in on address.

* 445 west 2nd Avenue, Vancouver, British Columbia

```{r}
## google: try address -> high zoom (works)
van_gg4 <- get_map(location='445 west 2nd Avenue, Vancouver, British Columbia', 
                   zoom=16,
                   maptype='satellite',
                   force=TRUE)
ggmap(van_gg4)
```



